\documentclass[a4paper,10pt]{article}
\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx, url, hyperref, palatino, tabularx, fontenc, inputenc, color, enumitem}
\definecolor{mygrey}{gray}{0.85}
\pagestyle{empty}
\newcommand{\resitem}[1]{\item #1}
\newcommand{\resheading}[1]{\vspace{0.5em} {\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1}}\end{minipage}}\vspace{0.5em}}
\newcommand{\ressubheading}[3]{\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r} \textbf{#1} & \textit{[#2]} \\ \end{tabular*}\vspace{-8pt}}
\begin{document}
\begin{center} \Large{\textbf{SAMPRITY GHOSH}} \end{center}
\vspace{2pt}
\begin{center}  Email: samprityghosh234@gmail.com | Phone: (+91) 9432932987 \end{center}
\begin{center} https://www.linkedin.com/in/samprity-ghosh/ | https://github.com/Samprity01 | https://samprityportfolio.netlify.app/ \end{center}
\resheading{Summary}
\resitem{Proficient in Full Stack Web development, AIML with a background in Computer Science Engineering. Hands-on experience in HTML5, Tailwind CSS, React.js, Next.js, JavaScript, and MySQL, MongoDB. Domain expertise in Full stack web development, MERN Stack, Machine Learning, Deep Learning, Data Analytics and Visualization.  Quite knowledgeable in QA. Honing strong analytical skills, decision-making, problem-solving abilities, with a learning mindset and proactive approach.}

\resheading{Projects}
\ressubheading{Invest.io – AI-Driven Stock Market Intelligence}{}{}
\begin{itemize}[nosep]
    \resitem{Developed a full-stack platform providing real-time fundamental analysis of Nifty-100 companies for smarter investment decisions.}
    \resitem{Technology used: (Frontend - HTML, CSS, Javascript, Bootstrap 5, Backend - Django, Database - MySQL, IDE - VS Code, Tools - Postman, Version Control - Github)}
\end{itemize}
\ressubheading{Workplace Diversity and Inclusion Analysis}{}{}
\begin{itemize}[nosep]
    \resitem{Conducted gender-focused data analysis using Python, highlighting hiring trends and performance biases. Utilized data cleaning, visualization to generate actionable insights.}
    \resitem{Delivered structured outputs in CSV for strategic decision-making. Key Skills: Data Analytics, Python, Visualization, Diversity Insights, Statistical Analysis.}
\end{itemize}
\ressubheading{Asset Value Forecasting – AI for Smart Investments}{Final Year}{}
\begin{itemize}[nosep]
    \resitem{Uses machine learning for asset price prediction, integrating historical data, real-time trends, and market sentiment analysis to provide highly accurate forecasts.}
    \resitem{The model is optimized for investment banking, hedge funds, and financial analysts looking for data-driven decision-making.}
    \resitem{Technology used: (Front- HTML, CSS, JAVASCRIPT, Back-end- Flask, AI models- RNN, LSTM (Time series Forecasting), NLP Integration (Market Sentiment Analysis), Database- MongoDB)}
\end{itemize}
\ressubheading{CodeInspector- AI driven Code Reviewer}{}{}
\begin{itemize}[nosep]
    \resitem{An AI-powered tool that reviews code for quality, security, and performance, generating detailed documentation for production.}
    \resitem{It streamlines development, aids testers with comprehensive reports, and ensures efficient code maintenance. (Frontend-React.js, Backend- Express.js, Database-MongoDB, AI- Gemoni 2.O)}
\end{itemize}

\resheading{Papers and Publications}
\resitem{Indian Journal of Natural Sciences ISSN: 0976 – 0997– “Branching Out to Safeguard India’s Tomato Crop: A Novel Decision Tree Approach for Late Blight Disease Prediction” [Accepted]}
\resitem{A study for identifying Autism Related Behavioral Patterns Using Cartoon Videos [Accepted]}
\resitem{Book Chapter – “Machine Learning and Deep Learning Solutions in Healthcare Survey” [Accepted]}
\resitem{An Multilingual chatbot Which supports Health symptoms resolved issues after Analyzing symptoms and also explains The reason by XAI .[Applied].}

\resheading{Certifications}
\resitem{Certificate of AIML under ARDENT COMPUTECH PVT.LTD}
\resitem{Certificate of Python under ARDENT COMPUTECH PVT.LTD}
\resitem{Certificate of C, C++, Java, DSA under APTECH PVT. LTD}
\resitem{Python Certificate from CodeChef}
\resitem{Generative AI certificate from Linkedin Learning}
\resitem{Certificate of Data Analytics From Linkedin Learning}

\resheading{Achievements}
\resitem{CodeSprint ’24 – Analytics Case Competition – JIS UNIVERSITY, Qualified Round-1 (Prototype Analysis) On Rank-11 local scope.}
\resitem{Hack-O-MED 2023 - Case Study Solution, Qualified Round-2}

\resheading{Interests}
\resitem{Exploring technologies and innovations}

\resheading{Education}
\ressubheading{BTECH IN COMPUTER SCIENCE}{JIS UNIVERSITY, Aug 2021 – June 2025}
\ressubheading{Higher Secondary Education}{Ramakrishna Vivekananda Mission Vidyabhawan, Jan 2020 – Jan 2021}
\ressubheading{Secondary Education}{Ramakrishna Vivekananda Mission Vidyabhawan, Jan 2017 – Jan 2018}

\resheading{Skills}
\resitem{Programming Languages: Python, Java, CPP, SQL, C}
\resitem{Libraries and Frameworks: NumPy, Pandas, React.js, Node.js}
\resitem{Data Visualization: Power BI, Excel}
\resitem{Expertise in: Machine Learning, Deep Learning, Full Stack web development, Data Analysis, Business analytics, Documentation}
\resitem{Cloud: AWS (Beginners)}

\resheading{Experience}
\ressubheading{Software Development Intern}{Bluestock Fintech, December 2024 – January 2025}
\begin{itemize}[nosep]
    \resitem{Working on a Financial Full stack site where I am associated as a Software Developer. Designed frontend and optimized SQL queries for database performance scoring, achieving confidence levels of 70–100\%.}
    \resitem{Tools used: (Frontend - HTML, CSS, Javascript, Bootstrap 5, Backend - Django, Database - MySQL, IDE - VS Code, Tools - Postman, Version Control- Github) | Completion Certificate}
\end{itemize}

\end{document}